# Yield Analysis

```{r}
suppressPackageStartupMessages({
  library("ggplot2")
  library("dplyr")
})
prices1 <- PROJ$db[["prices1"]]

```


## By Group

Yields and prices of the bonds, grouped into "North", "South", "Border" (Kentucky, Missouri), and "Union" government bonds.

Plot of the clean prices

```{r}
ggplot(prices1, aes(x = as.Date(date), y = price_clean_mean, group = series, color = group)) + geom_line()

```

Plot of the yields to maturity

```{r}
ggplot(prices1, aes(x = as.Date(date), y = ytm_mean, group = series, color = group)) + geom_line()

```

Plots of the current yields

```{r}
ggplot(prices1, aes(x = as.Date(date), y = current_yield_mean, group = series, color = group)) + geom_line()

```

## Government Bonds

```{r}
govt_bonds <- filter(prices1, group == "Union")

```

Plot of clean prices (gold),
```{r}
ggplot(govt_bonds, aes(x = as.Date(date), y = price_clean_mean, color= series)) + geom_line()

```

Plot of the yields to maturity
```{r}
ggplot(govt_bonds, aes(x = as.Date(date), y = ytm_mean, color= series)) + geom_line()

```

Plots without the one year notes which have unusual interest rates,
```{r}
ggplot(filter(govt_bonds, !grepl("oneyr", series)), aes(x = as.Date(date), y = ytm_mean, color= series)) + geom_line()

```

Plots of the current yields
```{r}
ggplot(govt_bonds, aes(x = as.Date(date), y = current_yield_mean, color= series)) + geom_line()

```



